Finding Bugs in JavaScript Engines with Differential Testing

### 2018-05-12 docs/google-research-awards-latam/main.tex
adding example. Igor, *please* double-check what I wrote and fill the gaps (references left to add)

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{subfigure}
% ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkaquamarine}{rgb}{0.2,0.4,0.3}
%% macros
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}

@@

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
demands of the community and these changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions.  Test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle for finding functional errors.

@@

\begin{wrapfigure}[12]{r}[0pt]{0.45\textwidth}
\vspace{-5ex}
%\begin{figure}[htbp]
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \label{fig:workflow}
  \caption{Fuzzing Infrastructure.}
%\end{figure}
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}) and whether or not coverage information
is taken into account in the fuzzing
process. Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer, instantiated to our problem. In our case, JS files are
provided as seeded inputs to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure needs to detect and discard syntactically invalid
inputs. Semantically invalid inputs are detected dynamically or with
linters. Once the input is found to be valid, the infrastructure
invokes the oracle to check correctness. In case either all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the given input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify those alarms in two groups: HI and LO. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. We found empirically that \Fix{XX\%} of the
warnings analyzed in the HI group were confirmed (see
Section~\ref{sec:results})

@@

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}

\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
  \vspace{-6ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}

Although there are many features yet to implement in our
infrastructure, the basic workflow described in
Section~\ref{sec:design} is already functional. Table~\ref{tab:bugs}
shows the list of bugs we reported on issue trackers of different
engines in the period of a month. So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.

Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that seven of the 13 JS files that manifested
discrepancies were produced with fuzzing (column ``Fuzz''). This
emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

@@

\item Explore different strategies to reduce the number of false
  positives. For example, mining issue trackers for similar bug
  reports.

\item Use our infrastructure to find bugs on
  WebAssembly~\cite{webassembly}, a new binary format already
  supported by major browsers. 
\end{itemize}

>>>>

% \usepackage{natbib}
% \setlength{\bibsep}{0pt plus 0.3ex}
\usepackage[margin=1cm]{caption}
\usepackage{titlesec}
\titlespacing*{\section}{0pt}{0.3\baselineskip}{0.3\baselineskip}
%,nohead,nofoot
%\usepackage[margin=1n,left=1cm,top=1cm,right=1.75cm,bottom=1.5cm]{geometry}
\usepackage[margin=1in,includeheadfoot,left=1cm,top=0.5cm,right=1.5cm,bottom=0.5cm]{geometry}
%\usepackage[margin=1in,includeheadfoot]{geometry}
\usepackage{url}
\usepackage{cite}
\usepackage{multirow}
\usepackage{lipsum}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig}
\usepackage{microtype}
\usepackage{hyperref}
\usepackage{listings}
\usepackage{subfigure}
% ADD THE FOLLOWING COUPLE LINES INTO YOUR PREAMBLE
\let\OLDthebibliography\thebibliography
\renewcommand\thebibliography[1]{
  \OLDthebibliography{#1}
  \setlength{\parskip}{0pt}
  \setlength{\itemsep}{0pt plus 0.3ex}
}

\usepackage[pdftex]{graphicx}
\usepackage{url}
\usepackage{color}
\usepackage{xcolor}
\definecolor{darkred}{rgb}{0.5,0,0}
\definecolor{darkgreen}{rgb}{0,0.5,0}
\definecolor{darkblue}{rgb}{0,0,0.5}
\definecolor{darkaquamarine}{rgb}{0.2,0.4,0.3}
%% macros
\newcommand{\ie}{i.e.}
\newcommand{\eg}{e.g.}
\newcommand{\Fix}[1]{\textbf{[[}{\color{red} #1}\textbf{]]}}
\newcommand{\Mar}[1]{\textbf{[[}{\color{blue} #1}\textbf{]]}}
\newcommand{\MAB}[1]{\textbf{[[}{\color{darkgreen} #1}\textbf{]]}}
\newcommand{\Igor}[1]{\textbf{[[}{\color{darkaquamarine} #1}\textbf{]]}}
\newcommand{\Comment}[1]{}
\newcommand{\CodeIn}[1]{{\small\texttt{#1}}}

@@

JavaScript (JS) is one of the most popular programming languages of
today~\cite{business-insider,stackify} largely because of its
widespread use on the web. As common in software, the JS specification
changes regularly\footnote{Recently, the specification went through a
  bigger change compared to prior releases, called by the name of
  ECMAScript6 (ES6)~\cite{es6-features}} to accommodate the pressing
demands of the community and these changes often entail sensible
changes in engine implementations~\cite{kangax} that could lead to
errors, including regressions. Automated test generation can help reduce the
cost of testing, but the lack of executable specifications is an
important obstacle. In particular, it is an obstable to find functional errors.

@@

\begin{wrapfigure}[10]{r}[0pt]{0.45\textwidth}
  \vspace{-5ex}
  \centering
  \includegraphics[trim=20 350 200 0,clip,width=0.45\textwidth]{google-awards-workflow}
  \caption{\label{fig:workflow}Fuzzing Infrastructure.}
  \vspace{-5ex}  
\end{wrapfigure}
Fuzzing is a popular technique to generate new test inputs from
existing inputs~\cite{fuzz-testing-history} with the typical goal of
finding crashes. Several fuzzing methods have been proposed in the
past, varying with respect to how new inputs are generated (\eg{},
coverage-based~\cite{afl,honggfuzz},
grammar-based~\cite{grammarinator,jsfunfuzz}, and
random-based~\cite{radamsa}) and whether or not coverage information
is taken into account in the fuzzing
process. Figure~\ref{fig:workflow} shows a generic pipeline of a
fuzzer, instantiated to our problem. Arrows indicate data flow; lines
with no arrow denote encapsulation. In our case, JS files are
provided as seeded inputs to bootstrap the process. These files can
originate from the test suites of the engine codebases or from the bug
reports in their issue trackers. The fuzzing infrastructure selects
randomly one of the inputs to fuzz with a given tool, say the
black-box fuzzer Radamsa~\cite{radamsa}. Each fuzzing iteration
produces a new file. For grammar-agnostic fuzzers, like Radamsa, the
infrastructure needs to detect and discard syntactically invalid
inputs. Semantically invalid inputs are detected dynamically or with
linters. Once the input is found to be valid, the infrastructure
invokes the oracle to check correctness. In case all engines
consider the test output consistent (\ie{}, all pass or all fail), the
infrastructure discards the corresponding input. Otherwise, it considers that
input as potentially fault-revealing and interesting. Currently, we
classify alarms in two groups: HI and LO. The HI group includes
those warnings that manifest execution errors spawned directly by the
test (or its close neighborhood) whereas the LO group includes the
rest of the warnings. We found empirically that \Fix{XX\%} of the
warnings analyzed in the HI group were confirmed (see
Section~\ref{sec:results})

@@

Although there are many features yet to implement in our
infrastructure, the basic workflow described in
Section~\ref{sec:design} is functional. This section shows preliminary
results providing some evidence that finding bugs in runtime engines is
promising. Table~\ref{tab:bugs} shows the list of bugs we reported on
issue trackers of different engines in the period of a month. For
example, bug \# 6 was manifested by the JS code \CodeIn{var a =
  \{valueOf:~function()\{return ``\textbackslash{}x00''\}\} assert(+a
  === 0)\}}\footnote{This is a Lithium-minimized~\cite{lithium}
  version of the fuzzed code.}. In the original version of this code the \CodeIn{valueOf} function returned
the empty string, whose integer representation according to the spec
should be zero\Fix{check part of spec to link}. The modified
code returns a string representation of an invalid hexadecimal
value. The engines should not be able to evaluate that string at
the assertion expression\Fix{explain why}. MS Chakra, however, is able to parse it
returning a null object. In addition, the test passes as it converts
null to zero.

\newcommand{\checkm}{Y}
\newcommand{\crossmark}{N}
\begin{wraptable}[16]{tr}[0pt]{0.5\textwidth}
  \vspace{-4ex}
  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    10, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}   \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        & \checkm &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \crossmark & Chakra & New & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
   \bottomrule     
  \end{tabular}
\end{wraptable}
So far, six of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that, with the exception of one case, all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any bug on SpiderMonkey and V8. Finally, it is
worth noting that seven of the 13 JS files that manifested
discrepancies were produced with fuzzing (column ``Fuzz''). This
emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from six different open
source engines, including a total of \Fix{38.9K} test files.

@@

\item Explore different strategies to reduce the number of false
  positives as to facilitate the inspection process. For example,
  mining issue trackers for similar bug reports is a candidate alternative.

\item Use our infrastructure to find bugs on
  WebAssembly~\cite{webassembly}, a new binary format already
  supported by major browsers. In principle, our infrastructure is
  agnostic to the runtime engine used. We are eager to explore other
  sources of bugs, especially in very new engines.

\end{itemize}
